---
title: "`r params$facility`  \nCT Reject Analysis \n `r substring(params$endDate,1,4)`"
author: "`r params$author`"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  word_document:
    reference_docx: "../../style/MIDAShWordReportStyle.docx"
  pdf_document:
    latex_engine: xelatex
    template: ../../style/midasTemplate.tex
    number_sections: yes
    pandoc_args: ["--variable", "graphics=yes",
                "--variable", "natbib=yes",
                "--variable", "geometry:margin=1in",
                "--variable", "compact-title:yes"]
    keep_tex: TRUE
link-citations: yes
bibliography: ../../style/references.bib
params:
  author: ''
  authorEmail: ''
  authorPhone: ''
  authorArea: ''
  facility: ''
  facilityID: ''
  rspp: Radiation Management Plan
  startDate: '20240101'
  endDate: '20241231'
  pediatric: FALSE
  localSummary: TRUE
  minStudyCount: 10
  
biblio-style: unsrt
---


```{r setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.pos="H")

library(plotly)
library(lubridate)
library(tidyverse)
library(magrittr)
library(huxtable)

# Load local settings
baseDir <- getwd()
baseDir <- str_sub(baseDir, 1, last(str_locate_all(baseDir, "MIDASh/")[[1]])[[2]])
source(paste0(baseDir,"config/settingPointers.R"))


# pdf report settings
plotSaveMethod <- "kaleido" # or orca, or html depending on preferences, setup, and desired output. Orca is deprecated
plotSaveUseServer <- F # TRUE Doesn't necessarily work with orca
plotSaveOverwrite = T # FALSE is mostly for when developing and only working on non-plot related issues

# Setup kaleido via reticulate
if (plotSaveMethod=="kaleido"){
  reticulate::use_condaenv("r-reticulate")
  #reticulate::conda_install('r-reticulate', 'plotly', channel = 'plotly') # Only required for initial install
  #reticulate::conda_install('r-reticulate','python-kaleido') # Only required for initial install
  reticulate::py_run_string("import sys")
}

colorSet <- list(good="#2ECC40",
                 ok="#FF851B",
                 bad="#FF4136")

```

<!-- All data initial data processing should go here -->

```{r date-processing, echo=FALSE, include=FALSE}
startDate <- ymd(params$startDate)

startDateString <- paste(day(startDate), month(startDate,label = T,abbr = T), year(startDate))

endDate <- ymd(params$endDate)
endDateString <- paste(day(endDate), month(endDate,label = T,abbr = T), year(endDate))
```

```{r data-gathering, include=FALSE}

# Load the data
loadCTCache()
processCTCachedData()
```

```{r load-drl-data, include=FALSE}
mod <- "CT"

mDrl <- drl[[mod]]
mStudyMap <- studyMap[[mod]]

# List of custom groups to include in analysis
customDRLCategories <- c("CTPA", "CTCA")

mStudyMap <- mStudyMap %>% filter(
  (custom_group %in% customDRLCategories) |
    (custom_group == "Not Applicable") |
    (is.na(custom_group))
)

```

<!-- This section might need to be edited to override any errors in your collected data -->

```{r site-specific-processing, include=FALSE}
#Overwrite institution name, because it is unreliably set at the modalities
ctQueriedData$institution_name = params$facility
ctStudyData$institution_name = params$facility

#Set the selection and reference data set
selectionList <- list("display_name"=c("Scanner 1", "Scanner 2", "Scanner 3", "Scanner 4", "Scanner 5"))
referenceList <- list("study_description"=c("all")
                      )

```




```{r collect-ctpa, include=F}

rejectAcqData <- ctQueriedData %>%
  filterDataToSelectionFilterSet(referenceList=referenceList,selectionList = selectionList) %>%
  arrange(study_instance_uid, irradiation_event_uid) %>%
    mutate(
      single_rotation = abs(nominal_total_collimation_width/scanning_length-1)<0.06,
      short_scan = nominal_total_collimation_width < 30) %>%
    mutate(
      ct_acquisition_type = if_else(single_rotation & short_scan & (ct_acquisition_type %in% c(NA, "Stationary Acquisition", "Sequenced Acquisition")),
                                     "Monitoring Acquisition",
                                     ct_acquisition_type)
    ) %>%
  mutate(is_monitoring = ct_acquisition_type=="Monitoring Acquisition") %>%
  group_by(study_instance_uid) %>%
  mutate(cutoff = ifelse(is_monitoring, row_number(), 999)) %>%
  mutate(cutoff = min(cutoff, na.rm=T)) %>%
  mutate(contrast_indication = row_number() > cutoff) %>%
  ungroup %>%
  filter(study_description == "CT ANGIOGRAPHY PULMONARY")
  


rejectAcqData %>%
  sliceMaxDLPPerStudy() %>%
  select(accession_number, study_instance_uid) %>%
  openxlsx::write.xlsx("ctpa_accessions_for_pacs_scripts.xlsx")




```



```{r addForeignVars, include=F}

# CTPA Vars should be basically static unless the protocol names change
ctpaVars <- openxlsx::read.xlsx("ctpa_varieties.xlsx")
ctpaVars$acquisition_protocol <- stringr::str_squish(ctpaVars$acquisition_protocol)

# CTPA WEDs should be updated intermittently
ctpaWeds <- openxlsx::read.xlsx("ctpa_with_wed_20250917.xlsx") %>%
  select(study_instance_uid, scout_wed) %>%
  filter(., !duplicated(study_instance_uid)) %>%
  mutate(wed = scout_wed/10)


ctpaInjection <- read_csv("ctpa_injection_data.csv")


```





```{r reject-processing, include=F}


ageBinning <- function(df) {
  age_bins = c(0, 18, 35, 50, 75, 200)
  df$age_bin <- cut(df$patient_age_decimal, age_bins)
  
  
  return(df)
}

sizeBinning <- function(df) {
  bins = c(0, 20, 25, 27.5, 30, 32.5, 37.5,999)
  df$size_bin <- cut(df$wed, bins)
  
  return(df)
}

weightBinning <- function(df) {
  bins = c(0, 25, 50, 75, 100, 125, 150, 175,200,225,250, 999)
  df$weight_bin <- cut(df$patient_weight_est, bins)
  
  return(df)
}

weightBinningFine <- function(df) {
  bins = seq(5,400,5)
  df$weight_bin_fine <- cut(df$patient_weight_est, bins)
  
  return(df)
}


rejectAcqData <- rejectAcqData %>%
  filter(study_date < "2025-09-12")


rejectAcqData <- rejectAcqData %>%
  left_join(ctpaVars,by = "acquisition_protocol") %>%
  left_join(ctpaWeds, by = "study_instance_uid") %>%
  filter(!is.na(group_name)) %>%
  group_by(study_instance_uid) %>%
  mutate(scout_protocol=acquisition_protocol[[1]]) %>%
  filter(ct_acquisition_type != "Constant Angle Acquisition") %>%
  mutate(target_helical=max(target_helical),
         target_axial=max(target_axial)) %>%
  mutate(temp_protocol=paste(unique(acquisition_protocol),sep = " / ", collapse = "/ ")) %>%
  mutate(first_protocol=first(acquisition_protocol)) %>%
  mutate(last_protocol=last(acquisition_protocol)) %>%
  ungroup %>%
  filter(!is_monitoring) %>%
  getCTAcquisitionTotals() %>%
  mutate(reject_flag=(helical_count > target_helical) | (axial_count > target_axial)) %>% 
  ageBinning %>%
  sizeBinning


rejectStudyData <- rejectAcqData %>%
  sliceMaxDLPPerStudy()


rejectStudyData <- rejectStudyData %>% filter(!duplicated(study_instance_uid))
rejectStudyData <- left_join(rejectStudyData,ctpaInjection) %>%
  select(-study_instance_uid, -`...1`)


rejectStudyData <- rejectStudyData %>%
  mutate(patient_weight_est = 8.623*exp(0.0079*scout_wed)) %>%
  weightBinning %>%
  weightBinningFine



```


```{r, include=F}

model <- glm(rejectStudyData$wed ~ rejectStudyData$contrast_injection.0.contrast)
summary(model)

```



# Purpose

This report investigates the reject rate of CT Pulmonary Angiography procedures performed at `r params$facility`.



# Executive Summary


# Results

## Reject rate by weight fine

```{r reject-summary-age, echo=F}
rejectStudyData %>% group_by(weight_bin_fine) %>%
  summarise(.groups="keep",
    reject_count = sum(reject_flag),
    total_count = n()
  ) %>%
  filter(total_count > params$minStudyCount) %>%
  mutate(reject_rate = round(reject_count/total_count,digits=3)) %>% 
  tidyTableNames() %>%view
  as_hux
                  
```
```{r reject-summary-age, echo=F}
rejectStudyData %>% group_by(weight_bin_fine) %>%
  summarise(.groups="keep",
    reject_count = sum(reject_flag),
    total_count = n()
  ) %>%
  filter(total_count > params$minStudyCount) %>%
  mutate(reject_rate = round(reject_count/total_count,digits=3)) %>% 
  mutate(weight_bin_)
  plot_ly() %>% plotly::add_markers(x=~weight_bin_fine, y=~reject_rate)
                  
```

## Reject rate by weight

```{r reject-summary-age, echo=F}
rejectStudyData %>% group_by(weight_bin, patient_sex) %>%
  summarise(.groups="keep",
    reject_count = sum(reject_flag),
    total_count = n()
  ) %>%
  filter(total_count > params$minStudyCount) %>%
  mutate(reject_rate = round(reject_count/total_count,digits=3)) %>% 
  tidyTableNames() %>%view
  as_hux
                  
```

## Reject rate by age

```{r reject-summary-age, echo=F}
rejectStudyData %>% group_by(age_bin) %>%
  summarise(.groups="keep",
    reject_count = sum(reject_flag),
    total_count = n()
  ) %>%
  filter(total_count > params$minStudyCount) %>%
  mutate(reject_rate = round(reject_count/total_count,digits=3)) %>% 
  tidyTableNames() %>%
  as_hux
                  
```




## Reject rate by age and gender

```{r reject-summary-age-gender, echo=F}
rejectStudyData %>% group_by(age_bin, patient_sex) %>%
  summarise(.groups="keep",
    reject_count = sum(reject_flag),
    total_count = n()
  ) %>%
  filter(total_count > params$minStudyCount) %>%
  mutate(reject_rate = round(reject_count/total_count,digits=3)) %>% 
  tidyTableNames() %>%
  as_hux
           

```


## Reject rate by size and gender

```{r reject-summary-size-gender, echo=F}
rejectStudyData %>% group_by(size_bin, patient_sex) %>%
  summarise(.groups="keep",
    reject_count = sum(reject_flag),
    total_count = n()
  ) %>%
  filter(total_count > params$minStudyCount) %>%
  mutate(reject_rate = round(reject_count/total_count,digits=3)) %>% 
  tidyTableNames() %>%
  as_hux
           

```


## Reject rate by age and initial protocol used

```{r reject-summary-protocol, echo=F}
rejectStudyData %>%
  group_by(age_bin, first_protocol) %>%
  summarise(.groups="keep",
    reject_count = sum(reject_flag),
    total_count = n()
  ) %>%
  filter(total_count > params$minStudyCount) %>%
  mutate(reject_rate = round(reject_count/total_count,digits=3)) %>% 
  tidyTableNames() %>%
  as_hux %>%
  set_font_size(9)
                  
```


## Reject rate by CT system

```{r reject-rate-by-system, echo=FALSE}
rejectStudyData %>%
  group_by(display_name) %>%
  summarise(.groups="keep",
    reject_count = sum(reject_flag),
    total_count = n()
  ) %>%
  filter(total_count > params$minStudyCount) %>%
  mutate(reject_rate = round(reject_count/total_count,digits=3)) %>% 
  tidyTableNames() %>%
  as_hux %>%
  set_font_size(11)
                  
```

## Reject rate by technologist

```{r reject-summary-tech, echo=F}
rejectStudyData %>% group_by(operator_name) %>%
  summarise(.groups="keep",
    reject_count = sum(reject_flag),
    total_count = n()
  ) %>%
  filter(total_count > params$minStudyCount) %>%
  mutate(reject_rate = round(reject_count/total_count,digits=3)) %>%
  filter(total_count > 20) %>%
  tidyTableNames() %>%
  as_hux
                  
```


## Reject rate by size and initial contrast injection

```{r reject-summary-contrast, echo=F}
rejectStudyData %>% group_by(size_bin, `contrast_injection.0.contrast`) %>%
  summarise(.groups="keep",
    reject_count = sum(reject_flag),
    total_count = n()
  ) %>%
  filter(total_count > params$minStudyCount) %>%
  mutate(reject_rate = round(reject_count/total_count,digits=3)) %>%
  filter(total_count > params$minStudyCount) %>%
  tidyTableNames() %>%
  as_hux
                  
```

# Contact

Please contact `r params$authorArea` with any queries.

`r params$authorEmail`

`r params$authorPhone`

\newpage

\appendix

# Method

## Data sources

Facility data was collected automatically from Radiation Dose Structured Reports. These reports contain key dose metrics for all CT studies conducted.

## X-ray systems

Radiation dose data has been obtained for all the systems shown in table 2.

```{r show-device-table, echo=FALSE}

tdfs <- rejectStudyData %>%
  group_by(display_name) %>%
  filter(row_number()==1) %>%
  filter(study_datetime >= startDate) %>%
  filter(study_datetime <= endDate) %>%
  select(display_name, institution_name, manufacturer, manufacturer_model_name)
names(tdfs) <- tdfs %>% names %>% tidyString()

tdfs %>%
  as_hux %>%
  theme_basic %>% 
  set_caption(paste("FL systems included in FRL survey at", params$facility))  %>%
  set_font_size(9)

```

## Acquisition Protocol details


```{r acquisition-protocol-table, echo=FALSE}

ctpaVars %>% 
  tidyTableNames() %>%
  as_hux() %>%
  theme_basic %>%
  set_caption("CTPA Acquisition Protocol details for acquisitions in the study period") %>%
  set_font_size(9)


```


## Data analysis

The following steps are taken:

* Acquisitions are sorted into Scouts, Helicals, Axials (including volumes), and Monitoring.
* Based on the acquisition protocol, the target number of helical and axial acquisitions is assigned to each group
* Where multiple acquisition protocols are used for a certain study, the highest value is used.
* Where any acquisition protocol other than those designated as strictly belonging to CTPA procedures is used, the study is ignored
* Where the number of helical or axial acquisitions exceeds the target values, the study is considered to involve a reject


```{r}
tt <- rejectStudyData %>% select(reject_flag, wed, size_bin, age_bin, patient_sex, patient_age_decimal, first_protocol, mean_ctdivol, contrast=`contrast_injection.0.contrast`) %>%
  filter(!is.na(wed)) %>%
  filter(patient_age_decimal > 18)


modelSex <- glm(reject_flag ~ patient_sex, data = tt, family = binomial)
#summary(modelSex)

modelWed <- glm(reject_flag ~ wed, data = tt, family = binomial)
#summary(modelWed)

modelAge <- glm(reject_flag ~ patient_age_decimal, data = tt, family = binomial)
#summary(modelAge)

modelSexWed <- glm(reject_flag ~ wed + patient_sex, data = tt, family = binomial)
#summary(modelSexWed)

modelAgeWed <- glm(reject_flag ~ patient_age_decimal + wed, data = tt, family = binomial)
#summary(modelAgeWed)

modelProtocol <- glm(reject_flag ~ first_protocol, data = tt, family = binomial)

modelProtocolWed <- glm(reject_flag ~ first_protocol+wed, data = tt, family = binomial)

modelAgeWedProtocol <- glm(reject_flag ~ first_protocol+wed+patient_age_decimal, data = tt, family = binomial)

modelAgeGenderWed <-  glm(reject_flag ~ patient_sex+wed+patient_age_decimal, data = tt, family = binomial)

modelContrast <- glm(reject_flag ~ contrast, data = tt, family = binomial)

modelSizeGenderContrast <- glm(reject_flag ~ patient_sex+wed+contrast, data = tt, family = binomial)

modelAgeGenderWedContrast <- glm(reject_flag ~ patient_age_decimal+patient_sex+wed+contrast, data = tt, family = binomial)


modelCTDI <-  glm(reject_flag ~ mean_ctdivol, data = tt, family = binomial)



models <- AIC(modelSex, modelWed, modelAge, modelSexWed, modelAgeWed, modelProtocol, modelProtocolWed, modelAgeWedProtocol, modelAgeGenderWed, modelCTDI, modelContrast, modelSizeGenderContrast,modelAgeGenderWedContrast)
models_df <- as_tibble(models)
models_df$model <- rownames(models)
models_df <- models_df %>% select(model, df, AIC)
models_df %>% as_hux




```



```{r}
rejectStudyData %>% openxlsx::write.xlsx("ctpaRepeatData.xlsx")
```



# References